Does Anybody Really Know What Time It Is?\\ Automating the Extraction of Date Scalars

### 2015-07-09 nlp.tex

@@

While custom production rules can be added to the existing grammar to exclude such expressions, this approach is not optimal as it leads to a rather large grammar that needs to account for every single semantically valid date-time sequence of terminal symbols. Rather, we modify the existing grammar with the following additional constraints to the \texttt{Day} terminal symbol for excluding such expressions:
\begin{itemize}
\item Restriction on the distribution of $30$ and $31$:
Months usually alternate between lengths of 30 and 31 days. We can use x mod 2 to get an alternating pattern of 1 and 0, then just add our constant base number of days:

@@

Now if we substitute this expression in the x + 1 dividend of Equarion $2$, we can invert the pattern using our mask:

@@

Equation $3$ is now added as a restriction to the production rule \begin{grammar} <Days> ::= NUMBER(1-31) \end{grammar}.
\item LeapYear Restriction on February 29.

@@

>>>>

(add technical detail on programming environment and parser used for grammar)

@@

While custom production rules can be added to the existing grammar to exclude such expressions, this approach is not optimal as it leads to a rather large grammar that needs to account for every single semantically valid date-time sequence of terminal symbols. Rather, we modify the existing grammar with the following additional constraints to the \texttt{Day} terminal symbol for excluding such expressions:

\begin{itemize}
\item Restriction on the distribution of $30$ and $31$:
Months usually alternate between lengths of 30 and 31 days. We can use x mod 2 to get an alternating pattern of 1 and 0, then just add our constant base number of days:

@@

Now if we substitute this expression in the x + 1 dividend of Equation $2$, we can invert the pattern using our mask:

@@

\item LeapYear Restriction for February:
While the above restriction applies to all months barring February, we also apply a constraint to the number of days for February, based on whether the year is leap year or not. For this, we define a new symbol in the grammar called \texttt{LeapYear}. If an expression containing the month `February' or any such variant (\textit{e.g.} `Feb', `2') with the day `29' and a year, would need to resolve the \texttt{Year} symbol to be a \texttt{LeapYear}, defined as:

\begin{equation}
\texttt{Year} \Mod 4 == 0
\end{equation}

@@

Equations $3$ and $4$ are now added as a constraint to the production rule \begin{grammar} <Days> ::= NUMBER(1-31) \end{grammar}.
